---
title: "DSS"
author: "Daniel Skubleny"
date: "03/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Libraries
```{r}
#install.packages("~/Path/DSS_1.3.tar", repos = NULL, type="source")
library(DSS)
library(readxl)
library(reshape2)
library(pheatmap)
library(stringr)
library(ggplot2)
library(ggpubr)

```

#Load data
```{r}
urlfile<-'https://raw.githubusercontent.com/skubleny/BOLD_100_Gastric_Organoid/main/Data/DSS_bold.csv'
DSS_bold <-read.csv(urlfile,stringsAsFactors = FALSE, header = TRUE, row.names = 1)

urlfile<-'https://raw.githubusercontent.com/skubleny/BOLD_100_Gastric_Organoid/main/Data/dDSS_bold_cancer.csv'
dDSS_bold_cancer <-read.csv(urlfile,stringsAsFactors = FALSE, header = TRUE, row.names = 1)

urlfile<-'https://raw.githubusercontent.com/skubleny/BOLD_100_Gastric_Organoid/main/Data/DSS_bold_wide_individual_dDSS.csv'
DSS_bold_wide_individual_dDSS <-read.csv(urlfile,stringsAsFactors = FALSE, header = TRUE, row.names = 1)

urlfile<-'https://raw.githubusercontent.com/skubleny/BOLD_100_Gastric_Organoid/main/Data/nanostring_data.csv'
nanostring_data <-read.csv(urlfile,stringsAsFactors = FALSE, header = TRUE, row.names = 1)

urlfile<-'https://raw.githubusercontent.com/skubleny/BOLD_100_Gastric_Organoid/main/Data/DSS_bold.csv'
DSS_bold <-read.csv(urlfile,stringsAsFactors = FALSE, header = TRUE, as.is = TRUE)


```

#////////Visualizing ic50 and DSS
#DSS vs IC50 
```{r}
DSS_bold$tissue = as.factor(DSS_bold$tissue)
levels(DSS_bold$tissue) <- c("Cancer", "Normal")

dss_ic50_facet = ggplot(DSS_bold, aes(x= IC50, y = DSS_3, fill=Drug.Name)) +
  geom_point(shape = 21, size = 3, colour="black", alpha=0.7) + 
  ggtitle("Drug Sensitivity Score vs IC50") +
  scale_fill_discrete(name = "Drug Name", label = c("BOLD", "FLOT", "BOLD + FLOT", "FOLFOX", "BOLD + FOLFOX")) +
  xlab("IC50 [nM]") +
  ylab("Drug Sensitivty Score") +
  facet_wrap(~tissue) +
  theme_bw() +
  theme(axis.text.x = element_text(colour="black", size = 14, angle=45, hjust=1)) +
                theme(axis.text.y = element_text(colour="black",size = 14)) + 
                theme(plot.title = element_text(colour="black", size=14,hjust = 0, vjust=0)) +
                theme(axis.title.x = element_text(colour="black", size =14, vjust = 0.05)) +
                theme(axis.title.y = element_text(colour="black", size=14)) +
                theme(strip.text = element_text(size=14)) +
                theme(legend.title = element_text(color = "black", size = 14),
                      legend.text = element_text(color = "black", size = 14),
                      legend.position = c(0.8,0.7),
                      legend.background = element_rect(size=0.5, linetype="solid",colour ="black",fill=alpha("white",0.7)))

ggsave("dss_ic50_facet.png", dss_ic50_facet, width=8, height=5.5)
ggsave("dss_ic50_facet.svg", dss_ic50_facet, width=6, height=4.5)

```
#DSS vs drug
```{r}
dss_drugname_tissuegroup = ggplot(DSS_bold, aes(x= Drug.Name, y = DSS_3, fill=tissue)) +
  geom_boxplot() + 
  ggtitle("Drug Sensitivity Score vs Drug Name") +
  scale_x_discrete(label = c("BOLD", "FLOT", "BOLD + FLOT", "FOLFOX", "BOLD + FOLFOX")) +
  scale_fill_manual(name="Tissue", label=c("Cancer", "Normal"), values = c("#E41A1C" ,"#377EB8")) +
  xlab("Drug Name") +
  ylab("Drug Sensitivty Score") +
  ylim(0,100) +
  theme_bw() +
  theme(axis.text.x = element_text(colour="black", size = 12, angle=45, hjust=1)) +
                theme(axis.text.y = element_text(colour="black",size = 12)) + 
                theme(plot.title = element_text(colour="black", size=14,hjust = 0, vjust=0)) +
                theme(axis.title.x = element_text(colour="black", size =14, vjust = 0.05)) +
                theme(axis.title.y = element_text(colour="black", size=14)) +
                theme(strip.text = element_text(size=14)) +
                theme(legend.title = element_text(color = "black", size = 14),
                      legend.text = element_text(color = "black", size = 14),
                      legend.position = c(0.9,0.8),
                      legend.background = element_rect(size=0.5, linetype="solid",colour ="black",fill=alpha("white",0.7)))

ggsave("dss_drugname_tissuegroup.png", dss_drugname_tissuegroup, width=8, height=4.5)
ggsave("dss_drugname_tissuegroup.svg", dss_drugname_tissuegroup, width=8, height=4.5)


dss_drugname_plot = ggplot(DSS_bold, aes(x= Drug.Name, y = DSS_3)) +
  geom_boxplot(fill = c(rep(c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3"), 2))) + 
  ggtitle("Drug Sensitivity Score vs Drug Name") +
  xlab("Drug Name") +
  ylab("Drug Sensitivty Score") +
  ylim(0,100) +
  stat_compare_means(size=5, label.y = 80, label.x = 2) + 
  scale_x_discrete(label = c("BOLD", "FLOT", "BOLD + FLOT", "FOLFOX", "BOLD + FOLFOX")) +
  facet_wrap(~tissue) +
  theme_bw() +
  theme(axis.text.x = element_text(colour="black", size = 14, angle=45, hjust=1)) +
                theme(axis.text.y = element_text(colour="black",size = 14)) + 
                theme(strip.text = element_text(size=14)) +
                theme(plot.title = element_text(colour="black", size=14,hjust = 0, vjust=0)) +
                theme(axis.title.x = element_text(colour="black", size =14, vjust = 0.05)) +
                theme(axis.title.y = element_text(colour="black", size=14)) +
                theme(legend.title = element_text(color = "black", size = 14),
                      legend.text = element_text(color = "black", size = 14),
                      legend.position = c(0.8,0.8),
                      legend.background = element_rect(size=0.5, linetype="solid",colour ="black",fill=alpha("white",0.7)))

ggsave("dss_drugname_plot.png", dss_drugname_plot, width=6, height=4.5)
ggsave("dss_drugname_plot.svg", dss_drugname_plot, width=6, height=4.5)

dunn.test::dunn.test(DSS_bold$DSS_3, DSS_bold$Drug.Name, method = "BH")
FSA::dunnTest(DSS_bold$DSS_3, DSS_bold$Drug.Name, method = "bh")

```
#DSS histogram
```{r}
DSS_bold_all = DSS_bold
DSS_bold_all$index = seq(nrow(DSS_bold_all))
DSS_bold_all = DSS_bold_all[order(DSS_bold_all$DSS_3, decreasing = TRUE),]  
order_id = DSS_bold_all$Patient.ID

dss_histogram = ggplot(DSS_bold_all, aes(x = reorder(index, -DSS_3), y = DSS_3, fill=Drug.Name)) +
  geom_bar(stat = "identity", position="dodge") + 
  scale_x_discrete(labels = order_id) +
  ggtitle("Drug Sensitivity Score Ranking") +
  xlab("Sample ID") +
  ylab("Drug Sensitivty Score") +
  theme_bw() +
  theme(axis.text.x = element_text(colour="black", size = 12, angle=45, hjust=1)) +
                theme(axis.text.y = element_text(colour="black",size = 12)) + 
                theme(plot.title = element_text(colour="black", size=12,hjust = 0, vjust=0)) +
                theme(axis.title.x = element_text(colour="black", size =12, vjust = 0.05)) +
                theme(axis.title.y = element_text(colour="black", size=12)) +
                theme(legend.title = element_text(color = "black", size = 12),
                      legend.text = element_text(color = "black", size = 12),
                      legend.position = c(0.8,0.6),
                      legend.background = element_rect(size=0.5, linetype="solid",colour ="black",fill=alpha("white",0.7)))

ggsave("dss_histogram.png", dss_histogram, width=12, height=4)
ggsave("dss_histogram.svg", dss_histogram, width=12, height=4)
```
#DSS Heatmap
```{r}
####heatmap
library(reshape2)
library(pheatmap)
DSS_bold_wide = dcast(DSS_bold, Patient.ID + tissue~Drug.Name, value.var="DSS_3" )

DSS_bold_wide = tibble::column_to_rownames(DSS_bold_wide, "Patient.ID")

cols= RColorBrewer::brewer.pal(9, "Reds")
pheatmap(DSS_bold_wide[,2:6], color= colorRampPalette(RColorBrewer::brewer.pal(9, "Reds"))(1000))

png("dss_heatmap.png", width = 6, height = 4, units = 'in', res = 300)
pheatmap(DSS_bold_wide[,2:6], color= colorRampPalette(RColorBrewer::brewer.pal(9, "Reds"))(1000))
dev.off()

svg("dss_heatmap.svg", width = 10, height = 6)
pheatmap(t(DSS_bold_wide[,2:6]), color= colorRampPalette(RColorBrewer::brewer.pal(9, "Reds"))(1000),
         labels_row=c("BOLD", "FLOT", "BOLD + FLOT", "FOLFOX", "BOLD + FOLFOX"),
         angle_col = 45,
         cellwidth = 24,
         cellheight = 12,
         treeheight_row = 25,
         treeheight_col = 25)
dev.off()

```
#Paired individual DSS per drug
```{r}
library(stringr)
#54,55,59,66,71,72,76

DSS_bold_wide_individual_dDSS = DSS_bold
DSS_bold_wide_individual_dDSS = dplyr::filter(DSS_bold_wide_individual_dDSS, !Patient.ID=="75N")
DSS_bold_wide_individual_dDSS = dplyr::filter(DSS_bold_wide_individual_dDSS, !Patient.ID=="77C")
DSS_bold_wide_individual_dDSS = dplyr::filter(DSS_bold_wide_individual_dDSS, !Patient.ID=="62C")
DSS_bold_wide_individual_dDSS = dplyr::filter(DSS_bold_wide_individual_dDSS, !Patient.ID=="64C")
DSS_bold_wide_individual_dDSS = dplyr::filter(DSS_bold_wide_individual_dDSS, !Patient.ID=="67C")

DSS_bold_wide_individual_dDSS$patient = str_sub(DSS_bold_wide_individual_dDSS$Patient.ID,1,nchar(DSS_bold_wide_individual_dDSS$Patient.ID)-1)
DSS_bold_wide_individual_dDSS$patient = as.factor(DSS_bold_wide_individual_dDSS$patient )

DSS_bold_wide_individual_dDSS = dcast(DSS_bold_wide_individual_dDSS,  patient + Drug.Name~tissue, value.var="DSS_3" )
DSS_bold_wide_individual_dDSS$dDSS = DSS_bold_wide_individual_dDSS$Cancer-DSS_bold_wide_individual_dDSS$Normal

DSS_bold_wide_individual_dDSS$index = seq(nrow(DSS_bold_wide_individual_dDSS))
DSS_bold_wide_individual_dDSS = DSS_bold_wide_individual_dDSS[order(DSS_bold_wide_individual_dDSS$dDSS, decreasing = TRUE),]  
organoid_id = DSS_bold_wide_individual_dDSS$patient
```
#Paired dDSS swimmer plot
```{r}
ddss_swimmer = ggplot(DSS_bold_wide_individual_dDSS, aes(x = reorder(index, -dDSS), y = dDSS, fill=Drug.Name)) +
  geom_bar(stat = "identity", position="dodge") + 
  scale_x_discrete(labels = organoid_id) +
  ggtitle("differential Drug Sensitivity Score Ranking") +
  scale_fill_discrete(name = "Drug Name", label = c("BOLD", "FLOT", "BOLD + FLOT", "FOLFOX", "BOLD + FOLFOX")) +
  xlab("Sample ID") +
  ylab("dDSS") +
  theme_bw() +
  theme(axis.text.x = element_text(colour="black", size = 12, angle=45, hjust=1)) +
                theme(axis.text.y = element_text(colour="black",size = 12)) + 
                theme(plot.title = element_text(colour="black", size=12,hjust = 0, vjust=0)) +
                theme(axis.title.x = element_text(colour="black", size =12, vjust = 0.05)) +
                theme(axis.title.y = element_text(colour="black", size=12)) +
                theme(legend.title = element_text(color = "black", size = 12),
                      legend.text = element_text(color = "black", size = 12),
                      legend.position = c(0.5,0.9),
                      legend.direction = "horizontal",
                      legend.background = element_rect(size=0.5, linetype="solid",colour ="black",fill=alpha("white",0.7)))

ggsave("ddss_swimmer.png", ddss_swimmer, width=8, height=4.5)
ggsave("ddss_swimmer.svg", ddss_swimmer, width=8, height=4.5)

```

#####dDSS analysis of paired samples
```{r}
dDSS_bold = DSS_bold
dDSS_bold_norm = dplyr::filter(dDSS_bold, tissue=="Normal")
dDSS_bold_cancer = dplyr::filter(dDSS_bold, tissue=="Cancer")

mean_bold = mean(dDSS_bold_norm[dDSS_bold_norm$Drug.Name=="BOLD",]$DSS_3)
mean_flot_bold = mean(dDSS_bold_norm[dDSS_bold_norm$Drug.Name=="FLOT_BOLD",]$DSS_3)
mean_folfox_bold = mean(dDSS_bold_norm[dDSS_bold_norm$Drug.Name=="FOLFOX_BOLD",]$DSS_3)
mean_flot = mean(dDSS_bold_norm[dDSS_bold_norm$Drug.Name=="FLOT",]$DSS_3)
mean_folfox = mean(dDSS_bold_norm[dDSS_bold_norm$Drug.Name=="FOLFOX",]$DSS_3)


dDSS_bold_cancer$control_DSS = c(rep(mean_bold, 11),rep(mean_flot_bold, 11),rep(mean_folfox_bold, 11),rep(mean_flot, 11),rep(mean_folfox, 11)) #11 is for the number of cancer samples
dDSS_bold_cancer$dDSS = dDSS_bold_cancer$DSS_3 -dDSS_bold_cancer$control_DSS

dDSS_bold_cancer$index = seq(nrow(dDSS_bold_cancer))
ggplot(dDSS_bold_cancer, aes(x = reorder(index, -dDSS), y = dDSS, fill=Drug.Name)) +
  geom_bar(stat = "identity", position="dodge")

ggplot(dDSS_bold_cancer, aes(x= Patient.ID, y = dDSS)) +
  geom_boxplot() 
kruskal.test(dDSS_bold_cancer$dDSS, dDSS_bold_cancer$Patient.ID)

ggplot(dDSS_bold_cancer, aes(x= Drug.Name, y = dDSS)) +
  geom_boxplot() 
kruskal.test(dDSS_bold_cancer$dDSS, dDSS_bold_cancer$Drug.Name)


ddss_paired_box_meancont = ggplot(dDSS_bold_cancer, aes(x= Drug.Name, y = dDSS, fill=Drug.Name)) +
  geom_boxplot(fill = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")) + 
  stat_compare_means(size=5, label.y = 15, label.x = 1) +
  ggtitle("differential Drug Sensitivity Score Ranking") +
  scale_x_discrete(name = "Drug Name", label = c("BOLD", "FLOT", "BOLD + FLOT", "FOLFOX", "BOLD + FOLFOX")) +
  ylab("dDSS") +
  theme_bw() +
  theme(axis.text.x = element_text(colour="black", size = 14, angle=45, hjust=1)) +
                theme(axis.text.y = element_text(colour="black",size = 14)) + 
                theme(plot.title = element_text(colour="black", size=14,hjust = 0, vjust=0)) +
                theme(axis.title.x = element_text(colour="black", size =14, vjust = 0.05)) +
                theme(axis.title.y = element_text(colour="black", size=14))

ggsave("ddss_paired_box_meancont.png", ddss_paired_box_meancont, width=6, height=4)
ggsave("ddss_paired_box_meancont.svg", ddss_paired_box_meancont, width=6, height=4)

dunn.test::dunn.test(dDSS_bold_cancer$dDSS, dDSS_bold_cancer$Drug.Name, method = "BH")
FSA::dunnTest(dDSS_bold_cancer$dDSS, dDSS_bold_cancer$Drug.Name, method = "bh")
```

#R synergy test
```{r}
library(BIGL)
library(rgl)
```

#Organize Data
```{r}
urlfile<-'https://raw.githubusercontent.com/skubleny/BOLD_100_Gastric_Organoid/main/Data/assay_results.xlsx'
bold_effect_FLOT = read.xlsx(urlfile, sheet="BOLD_nrmlzd_wide")
bold_effect_FLOT = dplyr::select(bold_effect_FLOT, -"FOLFOX_Dose")
bold_effect_FLOT = tidyr::gather(bold_effect_FLOT, ID, value, effect_1:effect_3, -c(Patient.ID, BOLD_Dose, FLOT_Dose))
bold_effect_FLOT = dplyr::select(bold_effect_FLOT, -"ID")


bold_effect_FOLFOX = read.xlsx(urlfile, sheet="BOLD_nrmlzd_wide")
bold_effect_FOLFOX = dplyr::select(bold_effect_FOLFOX, -"FLOT_Dose")
bold_effect_FOLFOX = tidyr::gather(bold_effect_FOLFOX, ID, value, effect_1:effect_3, -c(Patient.ID, BOLD_Dose, FOLFOX_Dose))
bold_effect_FOLFOX = dplyr::select(bold_effect_FOLFOX, -"ID")


FLOT_effect = read.xlsx(urlfile, sheet="FLOT_nrmlzd_wide")
FLOT_effect = tidyr::gather(FLOT_effect, ID, value, effect_1:effect_3, -c(Patient.ID, BOLD_Dose, FLOT_Dose))
FLOT_effect = dplyr::select(FLOT_effect, -"ID")

FOLFOX_effect = read.xlsx(urlfile, sheet="FOLFOX_nrmlzd_wide")
FOLFOX_effect = tidyr::gather(FOLFOX_effect, ID, value, effect_1:effect_3, -c(Patient.ID, BOLD_Dose, FOLFOX_Dose))
FOLFOX_effect = dplyr::select(FOLFOX_effect, -"ID")

bold_flot_combo = read.xlsx(urlfile, sheet="BOLD_FLOT_nrmlzd_wide")
bold_flot_combo = tidyr::gather(bold_flot_combo, ID, value, effect_1:effect_3, -c(Patient.ID, BOLD_Dose, FLOT_Dose))
bold_flot_combo = dplyr::select(bold_flot_combo, -"ID")

bold_folfox_combo = read.xlsx(urlfile, sheet="BOLD_FOLFOX_nrmlzd_wide")
bold_folfox_combo = tidyr::gather(bold_folfox_combo, ID, value, effect_1:effect_3, -c(Patient.ID, BOLD_Dose, FOLFOX_Dose))
bold_folfox_combo = dplyr::select(bold_folfox_combo, -"ID")

flot_isobol = rbind(bold_effect_FLOT, FLOT_effect)
flot_isobol = rbind(flot_isobol, bold_flot_combo)
colnames(flot_isobol) = c("Patient.ID","d1", "d2", "effect")
flot_isobol <- flot_isobol[, c("Patient.ID", "effect", "d1", "d2")]

folfox_isobol = rbind(bold_effect_FOLFOX, FOLFOX_effect)
folfox_isobol = rbind(folfox_isobol, bold_folfox_combo)
colnames(folfox_isobol) = c("Patient.ID","d1", "d2", "effect")
folfox_isobol <- folfox_isobol[, c("Patient.ID", "effect", "d1", "d2")]
```

##54C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="54C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_54Cflot = summary(rs)

isobologram(rs)
```
##55C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="55C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)

rs_55Cflot = summary(rs)
isobologram(rs)
```
##59C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="59C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_59Cflot = summary(rs)
isobologram(rs)
```
##62C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="62C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_62Cflot = summary(rs)
isobologram(rs)
```
##64C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="64C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)



rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_64Cflot = summary(rs)
isobologram(rs)
```
##66C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="66C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)



rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_66Cflot = summary(rs)
isobologram(rs)
```
##67C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="67C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)



rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_67Cflot = summary(rs)
isobologram(rs)
```
##71C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="71C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)



rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_71Cflot = summary(rs)
isobologram(rs)
```
##72C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="72C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_72Cflot = summary(rs)
isobologram(rs)
```
##76C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="76C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_76Cflot = summary(rs)
isobologram(rs)
```
##77C FLOT
```{r}
set.seed(99)

assay_data = dplyr::filter(flot_isobol, Patient.ID=="77C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
rs_77Cflot = summary(rs)
isobologram(rs)
```
##54C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="54C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##55C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="55C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)


assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##59C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="59C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##62C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="62C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##64C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="64C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##66C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="66C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##67C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="67C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##71C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="71C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##72C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="72C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##76C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="76C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```
##77C FOLFOX
```{r}
set.seed(99)
assay_data = dplyr::filter(folfox_isobol, Patient.ID=="77C")
assay_data = assay_data[,-1]
assay_data = na.omit(assay_data)

assay_data$effect = 100-assay_data$effect

fitMarginals(assay_data)
marginalFit <- fitMarginals(assay_data,"shared_asymptote" = FALSE,names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

marginalFit <- fitMarginals(assay_data, fixed = c("m1" = 100, "m2" = 100, "b"=0),"shared_asymptote" = FALSE,  names = c("BOLD", "FLOT"))
summary(marginalFit)
plot(marginalFit)

rs <- fitSurface(assay_data, marginalFit,
                 null_model = "loewe2",
                 method = "model",
                 B.CP = 50, statistic = "both", parallel = FALSE)
summary(rs)
isobologram(rs)
```


combo_nanostring_organoid <- read.csv("~/Documents/R projects/Gastric cancer ISD/ISDEvaluation-master/combo_nanostring_organoid.csv")
combo_nanostring_organoid = combo_nanostring_organoid[,-1]
#Organoid drug response 
```{r}

###Simple
cor_list <- by(nanostring_data[,c(2:5,7,19)], nanostring_data[,13], function(x) cor(x, method="pearson"))
cor_list = lapply(cor_list, function(x) x[(colnames(x) %in% c("DSS_3"))])
cor_list <- data.frame(ID = rep(names(cor_list), sapply(cor_list, length)),
                 Obs = unlist(cor_list))
cor_list$subtype = rep(c(paste(colnames(nanostring_data[,c(2:5,7,19)]))),5)

cor_list_wide = tidyr::spread(cor_list, subtype, Obs)
cor_list_wide = tibble::column_to_rownames(cor_list_wide,  "ID")
cor_list_wide = dplyr::select(cor_list_wide, -"DSS_3")

cols_dss_subtype = rev(RColorBrewer::brewer.pal(9, "RdBu"))
paletteLength = 1000
myBreaks_dss_subtype <- c(seq(min(cor_list_wide), 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(max(cor_list_wide)/paletteLength, max(cor_list_wide), length.out=floor(paletteLength/2)))

svg("dss_subtye_heatmap.svg", width = 6, height = 4)
pheatmap(cor_list_wide, 
         color=colorRampPalette(colors =cols_dss_subtype)(1000),
         breaks=myBreaks_dss_subtype,
         labels_row=c("BOLD", "FLOT", "BOLD + FLOT", "FOLFOX", "BOLD + FOLFOX"),
         labels_col=c("TME High", "CIN", "EBV", "GS", "MSI"),
         angle_col = 45,
         cellwidth = 36,
         cellheight = 24,
         treeheight_row = 25,
         treeheight_col = 25)
dev.off()

###HMISC rcorr

combo_nanostring_cor =   by(nanostring_data[,c(2:5,7,19)], nanostring_data[,13], function(x) Hmisc::rcorr(as.matrix(x)))

flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}

cor_list_df_bold = flattenCorrMatrix(combo_nanostring_cor$BOLD$r, combo_nanostring_cor$BOLD$P)
cor_list_df_bold = cor_list_df_bold %>% dplyr::filter(column== "DSS_3")

cor_list_df_flot = flattenCorrMatrix(combo_nanostring_cor$FLOT$r, combo_nanostring_cor$FLOT$P)
cor_list_df_flot = cor_list_df_flot %>% dplyr::filter(column== "DSS_3")

cor_list_df_FLOT_BOLD = flattenCorrMatrix(combo_nanostring_cor$FLOT_BOLD$r, combo_nanostring_cor$FLOT_BOLD$P)
cor_list_df_FLOT_BOLD = cor_list_df_FLOT_BOLD %>% dplyr::filter(column== "DSS_3")

cor_list_df_FOLFOX = flattenCorrMatrix(combo_nanostring_cor$FOLFOX$r, combo_nanostring_cor$FOLFOX$P)
cor_list_df_FOLFOX = cor_list_df_FOLFOX %>% dplyr::filter(column== "DSS_3")

cor_list_df_FOLFOX_BOLD = flattenCorrMatrix(combo_nanostring_cor$FOLFOX_BOLD$r, combo_nanostring_cor$FOLFOX_BOLD$P)
cor_list_df_FOLFOX_BOLD = cor_list_df_FOLFOX_BOLD %>% dplyr::filter(column== "DSS_3")

###NO SIGNIFICANT CORRELATIONS. 

##########


flot_bold = c(-9.6972,
-6.4444,
-7.0648,
-7.5049,
-9.9627,
-17.4927,
-10.2865,
12.1566,
10.4729,
-9.2612,
-9.3231)
folfox_bold = c(-3.7986,
-3.008151,
-5.876878,
-5.8256,
-6.3551,
-3.3792,
3.8674,
22.13649,
16.04297,
-9.2475,
-3.2113)


bigl_synergy = data.frame(flot_bold,folfox_bold)
bigl_synergy$sample_id = c("54C", "55C", "59C","62C","64C","66C","67C", "71C", "72C","76C","77C")
wilcox.test(bigl_synergy$flot_bold,bigl_synergy$folfox_bold)


bigl_synergy_long = tidyr::gather(bigl_synergy,drug, synergy, flot_bold:folfox_bold )


bigl_synergy_plot = ggplot(bigl_synergy_long, aes(x = drug, y=synergy, fill=drug)) +  
  geom_boxplot() +
  scale_x_discrete(name="Drug Combination", label=c("BOLD + FLOT", "BOLD + FOLFOX")) +
  ylab("Synergy") +
  ggtitle("BIGL Loewe Additivity") +
  scale_fill_manual(name="drug",label=c("a","b"), values=c("#4DAF4A", "#984EA3")) +
  stat_compare_means(size=5,label.y = 18) +
  theme_bw() +
  theme(axis.text.x = element_text(colour="black", size = 14)) +
                theme(axis.text.y = element_text(colour="black",size = 14)) + 
                theme(plot.title = element_text(colour="black", size=14,hjust = 0, vjust=0)) +
                theme(axis.title.x = element_text(colour="black", size =14, vjust = 0.05)) +
                theme(axis.title.y = element_text(colour="black", size=14)) +
                theme(strip.text = element_text(size=14)) +
                theme(legend.title = element_text(color = "black", size = 14),
                      legend.text = element_text(color = "black", size = 14),
                      legend.position = "none",
                      legend.background = element_rect(size=0.5, linetype="solid",colour ="black",fill=alpha("white",0.7)))

ggsave("bigl_synergy_plot.svg", bigl_synergy_plot, width=5, height=4)


bigl_synergy_subtype = merge(bigl_synergy, nanostring_data, by="sample_id")


bigl_synergy_subtype_long = tidyr::gather(bigl_synergy_subtype,subtype, subtype_score, c("STAD_CIN","STAD_EBV","STAD_GS","STAD_MSI", "High_cal" ))

bigl_synergy_subtype_long$subtype = as.factor(bigl_synergy_subtype_long$subtype)
levels(bigl_synergy_subtype_long$subtype)= c("TME High", "CIN", "EBV", "GS", "MSI")

#Facet plot
folfox_bold_subtype = ggplot(bigl_synergy_subtype_long, aes(x=subtype_score, y=folfox_bold)) + 
  ylab("BIGL Overall Effect") +
  xlab("Subtype Score") +
  ggtitle("BIGL Overall Effect vs. Molecular Subtype for BOLD + FOLFOX") +
  geom_smooth(method="lm", se=FALSE, colour="gray", size=1.5) +
  geom_point(size=3) + 
  ylim(-20,25) +
  stat_cor(size=4.5,method="pearson", label.y=-15,vjust=0.5) + 
  theme_bw() +
  theme(axis.text.x = element_text(colour="black", size = 14, angle=45, hjust=1)) +
                theme(axis.text.y = element_text(colour="black",size = 14)) + 
                theme(plot.title = element_text(colour="black", size=14,hjust = 0, vjust=0)) +
                theme(axis.title.x = element_text(colour="black", size =14, vjust = 0.05)) +
                theme(axis.title.y = element_text(colour="black", size=14)) +
                theme(strip.text = element_text(size=14)) +
                theme(legend.title = element_text(color = "black", size = 14),
                      legend.text = element_text(color = "black", size = 14),
                      legend.position = c(0.8,0.6),
                      legend.background = element_rect(size=0.5, linetype="solid",colour ="black",fill=alpha("white",0.7))) +
  facet_grid(~subtype) 

ggsave("folfox_bold_subtype.svg", folfox_bold_subtype, width=10, height=3)

#Facet plot 2
flot_bold_subtype = ggplot(bigl_synergy_subtype_long, aes(x=subtype_score, y=flot_bold)) + 
  ylab("BIGL Overall Effect") +
  xlab("Subtype Score") +
  ggtitle("BIGL Overall Effect vs. Molecular Subtype for BOLD + FLOT") +
  geom_smooth(method="lm", se=FALSE, colour="gray", size=1.5) +
  geom_point(size=3) + 
  ylim(-20,25) +
  stat_cor(size=4.5,method="pearson", label.y=20,vjust=0.5) + 
  theme_bw() +
  theme(axis.text.x = element_text(colour="black", size = 14, angle=45, hjust=1)) +
                theme(axis.text.y = element_text(colour="black",size = 14)) + 
                theme(plot.title = element_text(colour="black", size=14,hjust = 0, vjust=0)) +
                theme(axis.title.x = element_text(colour="black", size =14, vjust = 0.05)) +
                theme(axis.title.y = element_text(colour="black", size=14)) +
                theme(strip.text = element_text(size=14)) +
                theme(legend.title = element_text(color = "black", size = 14),
                      legend.text = element_text(color = "black", size = 14),
                      legend.position = c(0.8,0.6),
                      legend.background = element_rect(size=0.5, linetype="solid",colour ="black",fill=alpha("white",0.7))) +
  facet_grid(~subtype) 
ggsave("flot_bold_subtype.svg", flot_bold_subtype, width=10, height=3)


```

